---
title: "Tugas7_Statistika C_5026211056_Kurniaman Andreas Zega"
output: html_document
date: '2022-05-18'
---
## Numerical Data
## Source
```{r load-data}
download.file("http://www.openintro.org/stat/data/nc.RData", destfile = "nc.RData")
load("nc.RData")
```
## 1
Calculate a 95% confidence interval for the average length of pregnancies 
(`weeks`) and interpret it in context. Note that since you're doing inference 
on a single population parameter, there is no explanatory variable, so you can
omit the `x` variable from the function.

##Jawaban
```{r 95% confidence level}
inference(y = nc$weeks, est = "mean", type = "ci", null = 0,
alternative = "twosided", method = "theoretical", conflevel = 0.95)
```
Dari perhitungan dan grafik di atas pada confidence level sebesar 95%, dihasilkan rata-rata dari lama waktu hamil adalah berkisar dari 38,1528 - 38,5165 minggu.

## 2
Calculate a new confidence interval for the same parameter at the 90% 
confidence level. You can change the confidence level by adding a new argument to the function: `conflevel = 0.90`.
##Jawaban
```{r 90-conflvl}
inference(y = nc$weeks, est = "mean", type = "ci", method = "theoretical", conflevel = 0.90)
```
Dari perhitungan dan grafik di atas pada confidence level sebesar 90%, dihasilkan rata-rata dari lama waktu hamil berkisar dari 38,182 - 38,4873 minggu.

## 3
Conduct a hypothesis test evaluating whether the average weight gained by 
younger mothers is different than the average weight gained by mature mothers.
##Jawaban
```{r mature young gainedwght}
inference(y = nc$gained, x = nc$mature, est = "mean", type = "ht", null = 0, alternative = "twosided", method = "theoretical")
```
Berdasarkan perhitungan dan grafik di atas, p-value-nya bernilai 0,1686 dimana nilainya lebih besar dari nilai Alpha yang hanya sebesar 0,05. Dengan demikian, dapat disimpulkan bahwa tidak ada perbedaan pertambahan berat badan yang cukup signifikan antara younger moms dan mature moms.

## 4
Now, a non-inference task: Determine the age cutoff for younger and mature 
mothers. Use a method of your choice, and explain how your method works.
##Jawaban
```{r age-cutoff}
c(min(subset(nc, mature == 'younger mom')$mage),max(subset(nc, mature == 'younger mom')$mage))
c(min(subset(nc, mature != 'younger mom')$mage),max(subset(nc, mature == 'mature mom')$mage))
```
Dari data yang didapat, Umur younger mom berkisar dari rentang 13-34 tahun sedangkan untuk mature mom berkisar dari rentang 35-50 tahun. Informasi ini didapat dengan melakukan subset pada younger mom dan mature mom serta melihat nilai umur terkecil dan terbesar dari masing-masing kategori.

## 5
Pick a pair of numerical and categorical variables and come up with a 
research question evaluating the relationship between these variables. 
Formulate the question in a way that it can be answered using a hypothesis test and/or a confidence interval. Answer your question using the `inference` function, report the statistical results, and also provide an explanation in plain language.
##Jawaban
Research question : Apakah kebiasaan merokok pada ibu yang sedang hamil mempengerahui lama waktu kehamilan?
```{r weeks-habit}
inference(y = nc$weeks, x = nc$habit, est = "mean", type = "ht", null = 0,
alternative = "twosided", method = "theoretical")
```
Dari perhitungan yang telah dilakukan, didapatkan bahwa p-value-nya bernilai 0,6030 yang mana lebih besar daripada nilai Alpha sebesar 0,05. Dengan begitu, dapat disimpulkan bahwa tidak perbedaan cukup signifikan pada lama masa kehamilan pada ibu yang merokok dengan yang tidak merokok.
