---
title: "Tugas5_Statistika C_5026211056_Kurniaman Andreas Zega"
output: html_document
date: '2022-04-27'
---

# SUMBER DATA
```{r load-data}
download.file("http://www.openintro.org/stat/data/ames.RData", destfile = "ames.RData")
load("ames.RData")
```
```{r source}
population <- ames$Gr.Liv.Area
samp <- sample(population, 60)
samp_mean <- mean(samp)
samp_sd <- sd(samp)
```

#ON YOUR OWN 1
Using the following function (which was downloaded with the data set), 
plot all intervals. What proportion of your confidence intervals include 
the true population mean? Is this proportion exactly equal to the 
confidence level? If not, explain why.
##Jawaban
``` {r explain proportion}
for(i in 1:50){
  samp <- sample(population, 60) 
  samp_mean[i] <- mean(samp)    
  samp_sd[i] <- sd(samp)    
}
lower_vector <- samp_mean - 1.96 * samp_sd / sqrt(60) 
upper_vector <- samp_mean + 1.96 * samp_sd / sqrt(60)
plot_ci(lower_vector, upper_vector, mean(population))
```
Dari plot yang ditampilkan,terdapat 4 dari 50 interval yang tidak mencakup nilai mu yakni 1499,6904. Untuk proporsi sendiri adalah sebesar 92% dimana nilainya tidak sama dengan confidence level. Untuk kasus ini, nilai confidence level dapat dianggap sebagai sebuah probabilitas yang mencakup true population mean.

# ON YOUR OWN 2
Pick a confidence level of your choosing, provided it is not 95%. What is 
the appropriate critical value?
##Jawaban 2
``` {r appropriate critical value}
cl <- 99
alpha <- 1-(cl/100)
cp <- 1-(alpha/2) 
critical_value <- qnorm(cp)
critical_value
```

# ON YOUR OWN 3
Calculate 50 confidence intervals at the confidence level you chose in the 
previous question. You do not need to obtain new samples, simply calculate 
new intervals based on the sample means and standard deviations you have 
already collected. Using the `plot_ci` function, plot all intervals and 
calculate the proportion of intervals that include the true population 
mean. How does this percentage compare to the confidence level selected for
the intervals?
## Jawaban 
```{r compare}
for(i in 1:50){
  samp <- sample(population, 60) 
  samp_mean[i] <- mean(samp)    
  samp_sd[i] <- sd(samp)    
}
lower_vector <- samp_mean - critical_value * samp_sd / sqrt(60) 
upper_vector <- samp_mean + critical_value * samp_sd / sqrt(60)
plot_ci(lower_vector, upper_vector, mean(population))
```
Dari plot yang ditampilkan, 1 dari 50 interval tidak mencakup nilai mu yakni mu-nya sebesar 1499,6904. Untuk proporsi sendiri sebesar 98% dimana nilainya lebih rendah dari confidence level yang baru yaitu 99%.